---
title: "Introduction to PhysiMineR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to PhysiMineR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(PhysiMineR)
```

## Overview

**PhysiMineR** provides a tidy, end-to-end workflow for importing, cleaning, and
analysing upper gastrointestinal physiological test data.  The three core test
types are:

| Test | Functions |
|------|-----------|
| High-resolution manometry (HRM) | `HRMCleanUp1()`, `HRMSwallowSummary()`, `HRMDiagnoses()` |
| Ambulatory pH-impedance | `dataImpClean()`, `dataImpSymptoms()`, `GORD_AcidImp_Lyon()` |
| Wireless pH capsule (BRAVO) | `dataBRAVOClean()`, `dataBRAVODayLabeller()`, `GORD_AcidBRAVO_Lyon()` |

---

## 1. BRAVO wireless pH capsule

### 1.1 Import and clean

```{r bravo-clean, eval=FALSE}
library(PhysiMineR)

day12 <- read.csv("BravoDay1And2.csv")
day34 <- read.csv("BravoDay3And4.csv")
total <- read.csv("BRAVOTotal.csv")

# Merge the three raw exports on the shared BRAVO study ID
raw_bravo <- merge(day12, day34, by = "BravoID", all = TRUE) |>
             merge(total, by = "BravoID", all = TRUE)

# Standardise column types, drop duplicates
clean_bravo <- dataBRAVOClean(raw_bravo)
```

### 1.2 Label per-day AET columns

```{r bravo-label, eval=FALSE}
labelled_bravo <- dataBRAVODayLabeller(clean_bravo,
                                        id_col   = "HospNum_Id",
                                        date_col = "VisitDate")
# New columns: bravoDay1 … bravoDay6, bravoNDays
```

### 1.3 Classify with Lyon Consensus 2.0

```{r bravo-lyon, eval=TRUE}
# Synthetic example data
df <- data.frame(
  HospNum_Id = c("A001", "A002", "A003", "A004"),
  bravoDay1  = c(7.2,  3.1,  5.0,  6.5),
  bravoDay2  = c(6.8,  2.9,  4.5,  5.8),
  bravoDay3  = c(7.5,  3.5,  4.8,  NA ),
  bravoDay4  = c(6.1,  3.0,  5.2,  NA ),
  bravoNDays = c(4,    4,    4,    2  )
)

classified <- GORD_AcidBRAVO_Lyon(df)
classified[, c("HospNum_Id", "AcidRefluxBRAVO_Lyon",
               "AcidRefluxBRAVO", "AcidRefluxBRAVOTotalOnly")]
```

**Lyon Consensus 2.0 thresholds applied:**

- AET > 6% on ≥ 2 days → **Conclusive GORD**
- AET < 4% on all available days → **GORD excluded**
- All other patterns → **Inconclusive**

---

## 2. Ambulatory pH-impedance monitoring

### 2.1 Clean merged data

```{r imp-clean, eval=FALSE}
imp  <- read.csv("Impedance2.csv")
symp <- read.csv("Imp_Symp.csv")
raw  <- merge(imp, symp, by = "Imp_Id", all = TRUE)
clean_imp <- dataImpClean(raw)
```

### 2.2 Classify with Lyon Consensus 2.0

```{r imp-lyon, eval=TRUE}
df_imp <- data.frame(
  HospNum_Id = c("B001", "B002", "B003", "B004"),
  MainAcidExpTotalClearanceChannelPercentTime = c(8.2, 5.1, 2.8, 4.9),
  M1_av      = c(1800, 2500, 3100, 2000),   # MNBI
  pspw_index = c(45,   70,   80,   55)       # PSPW %
)

out_imp <- GORD_AcidImp_Lyon(df_imp,
                              mnbi_col = "M1_av",
                              pspw_col = "pspw_index")
out_imp[, c("HospNum_Id", "AcidReflux_Lyon", "AcidReflux_Imp")]
```

In the inconclusive (borderline) zone (AET 4–6%), patients with MNBI < 2292 Ω
or PSPW index < 61% are upgraded to **Conclusive GORD (adjunctive)**.

---

## 3. High-resolution manometry

### 3.1 Clean HRM data

```{r hrm-clean, eval=FALSE}
main     <- read.csv("HRMImportMain.csv")
swallows <- read.csv("HRMImportSwallows.csv")
# Remove per-swallow raw trace columns
swallows <- swallows[, !grepl("Num\\d+", names(swallows))]
merged   <- merge(main, swallows, by = "HRM_Id", all = TRUE)
clean_hrm <- HRMCleanUp1(merged)
```

### 3.2 Diagnose with Chicago Classification v4.0

```{r hrm-cc4, eval=TRUE}
df_hrm <- data.frame(
  HRM_Id = c("H001", "H002", "H003", "H004", "H005", "H006"),
  ResidualmeanmmHg             = c(20,  18,   8,  6,  10,  12),
  failedChicagoClassification  = c(100, 30,   0,  100, 80,   0),
  panesophagealpressurization  = c(0,   25,   0,  0,   0,    0),
  prematurecontraction         = c(0,    0,  25,  0,   0,    0),
  rapidcontraction             = c(0,    0,   0,  0,   5,   25),
  DistalcontractileintegralmeanmmHgcms = c(50, 300, 1200, 60, 200, 9000),
  largebreaks                  = c(0,    0,   0,  0,  55,   0),
  smallbreaks                  = c(0,    0,   0,  0,   0,   0),
  Simultaneous                 = c(0,    0,   0,  0,   0,   0)
)

result <- HRMDiagnoses(df_hrm)
result[, c("HRM_Id", "ChicagoV4Diagnosis", "ChicagoV4DiagnosisGroup")]
```

---

## 4. Cross-test merging

When combining tests from the same patient, use `testMerge()` to select the
pair of studies that are closest in time:

```{r merge-ex, eval=TRUE}
hrm <- data.frame(
  HospNum_Id  = c("A", "A", "B"),
  VisitDate.x = as.Date(c("2020-01-01", "2021-06-01", "2020-03-01")),
  IRP = c(8, 9, 12)
)
bravo <- data.frame(
  HospNum_Id  = c("A", "B"),
  VisitDate.y = as.Date(c("2020-01-15", "2020-03-10")),
  AET_day1 = c(7.2, 3.1)
)
# Patient A has two HRM studies; the one closest to the BRAVO date is chosen
testMerge(hrm, bravo)
```

Use `max_days_apart` to enforce a maximum allowed interval between tests:

```{r merge-ex2, eval=FALSE}
testMerge(AllHRM, AllBravo, max_days_apart = 365)
```

---

## 5. References

- Gyawali CP, Kahrilas PJ, Savarino E, et al. (2021). Modern diagnosis of GERD:
  the Lyon Consensus. *Gut*, 70(7), 1351–1362.
  doi:10.1136/gutjnl-2020-323270

- Yadlapati R, Kahrilas PJ, Fox MR, et al. (2021). Esophageal motility disorders
  on high-resolution manometry: Chicago Classification version 4.0.
  *Neurogastroenterology & Motility*, 33(1), e14058.
  doi:10.1111/nmo.14058
