---
title: "FundoplicationFailedPeristalsis"
author: "Sebastian Zeki"
date: "20/11/2018"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

**$\color{red}{\text{B.Introductory sentence 1: Define the disease condition}}$.**
**$\color{red}{\text{C.Introductory sentence 2: The overview of the disease condition}}$.**
**$\color{red}{\text{D.Introductory sentence 3: The problem being addressed}}$.**

1. Aperistaltic oesophagus is a term that covers all conditions where achalasia is absent and there is no peristaltic activity
2. Aperistaltic oesophagus remains a difficult condition to treat with no specific and effective treatments
3. The number of non-achalasia aperistaltic oesophagus patients is unknown.
4. Although often isolated from outpatients in veterinary clinics, there is concern that MRSP follows a veterinary-hospital associated epidemiology


```{r Introduction}

```

## Aim
**eg** The aim of the study was to assess the number of patients with aperistaltic oesophagus without achalasia and ascertain their demographics


```{r Aim}
```



## Methods


**$\color{red}{\text{E.Define the Dates}}$.**
**$\color{red}{\text{F.Define the Location}}$.**
**$\color{red}{\text{F.Define the Eligibility}}$.**
**$\color{red}{\text{F.Define the Exclusion}}$.**
**$\color{red}{\text{G.Define the Sampling}}$.**
**$\color{red}{\text{H.Define the data cleaning methodology methods}}$.**

1. Get the dates from the minimum of the VisitDate column `r 1+1 `

2. Standard sentence here about GSTT: The results of high resolution studies performed in patients with cough as part of the presenting complaint to the gastroenterology service at Guy's and St Thomas' NHS Trust were examined retrospectively between June 2008 and January 2018. 

3. All patients selected were adults over the age of 18. Ethics was approved (IRAS number) and by the local ethics board.

4. Patients with incomplete data sets were exluded from the study. Where x was not available fromt the report, the raw file was located and manually analysed

5. Patients were selected according to Chicago Classification v3. Patients symptoms were selected from self reporting at impedance if this was done at the same time as high resolution manometry. If this was not the case then the symptoms were extracted either from the final report summarising the patient's condition and physiological diagnosis, or from the clinicians details when ordering the investigation.

6. This involves how the relevant columns were accordionised (eg categorising the patients/and how subgroups were formed).



```{r Acquisition}
library(PhysiMineR)
library(DiagrammeR)
library(CodeDepends)
library(tidyverse)
library(readxl)
library(EndoMineR)
library(dplyr)
library(kableExtra)


######################################### Data acquisiton######################################### 
source("/home/rstudio/PhysiMineR/R/sourcing_Data/PhysiData_Acq.R")

######################################### Data cleaning & Data merging######################################### 
source("/home/rstudio/PhysiMineR/R/sourcing_Data/PhysiData_Clean.R")

######################################### Data accordionisation######################################### 
source("/home/rstudio/PhysiMineR/R/sourcing_Data/PhysiData_Accordion.R")
```

```{r Forking}
######################################### Data forking (filtering and subsetting) #########################

#Get the fundoplication data

FundoplicationData <- read_excel("/home/rstudio/PhysiMineR/data/FundoplicationHospitalNums.xlsx")

names(FundoplicationData)<-c("HospNum_Id")



#Get all the HRM which are 100% failed
Aperistaltic_HRMImportMain<-HRMImportMain[HRMImportMain$failedChicagoClassification>99,]
#Get the HRM for all the Fundoplication patients
HRM_In_Fundoplication<-filter(Aperistaltic_HRMImportMain, HospNum_Id %in% FundoplicationData$HospNum_Id)




#Get the fundoplication 

```

```{r DataLinkage}


```

```{r DataPreparation}

#Really exploratory data analysis
#Exploratory data analysis- use Data Explorer package or GGally package
######Univariate analysis....
#Show all the missing data in each column
#Overall things to report in multivariate analysis from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5457877/

#(1) Selection of independent variables; 
#(2) Fitting procedure; 
#(3) Coding of variables; 
#(4) Interactions; 
#(5) Collinearity; 
#(6) Statistical significance (OR, 95% confidence interval [CI], P value); 
#(7) Goodness-of-fit; 
#(8) Checking for outliers; 
#(9) Complete identification of the statistical software application that was used; 
#(10) Sufficient events (>10) per variable; 
#(11) Participation of statisticians and epidemiologists; and 
#(12) Conformity with linear gradient.


library(DataExplorer)

#Steps:
#1. Get rid of bad columns with missing data

#Tells you which columns have the most missing data so they can be excluded
missing<-profile_missing(HRM_In_Fundoplication)

#Only <10% for each row missing data is accepted 
BravoAndHRMNoMissing<-missing[!grepl("Bad|Remove",missing$group),]

#Pick the columns with good data in them from this set
BravoAndHRMNoMissing<-BravoAndHRM[,match(as.character(BravoAndHRMNoMissing$feature),names(BravoAndHRM))]
                                                                               
                                                                               
library(psych)
#Only select the numerical variables




#3. Get some basic descriptive stats:
rr<-describe(HRM_In_Fundoplication)

#4. Get rid of bad outliers

#5. Transform variables
```

```{r PrelimAnalysisHRM}


#Select HRM only. Also get rid of DistalLESfromnarescm,ProximalLESfromnarescm,EsophageallengthLESUEScenterscm as these are colinear and reflect length of oesophagus altogether)

#4. Variable selection- choose HRM variables only here. Got rid of BasalrespiratorymeanmmHg,ContractileFrontVelocity,HiatusHernia and most oesophageal length measurements because of colinearity concerns with other variables
BravoAndHRMNoMissingFinal<-BravoAndHRMNoMissing %>%
  ungroup()%>%
  select(IntraabdominalLESlengthcm,
         Hiatalhernia,
         LOS_relax,
BasalrespiratoryminmmHg,
ResidualmeanmmHg,
DistalcontractileintegralmeanmmHgcms,
IntraboluspressureATLESRmmHg,
Distallatency,
failedChicagoClassification,
panesophagealpressurization,
largebreaks,
prematurecontraction,
rapidcontraction,
smallbreaks, 
AcidRefluxBRAVO)

#Check for multicolinearity
library("PerformanceAnalytics")
chart.Correlation(HRM_In_Fundoplication, histogram=TRUE, pch=1)
#Exploratory data analysis:
create_report(BravoAndHRMNoMissingFinal)

#Consider changing variables and repeat step 4


```

```{r HRM_MultipleLogRegression}

library(MASS)
# Fit the full model 
data<-na.omit(BravoAndHRMNoMissingFinal)
full.model <- glm(AcidRefluxBRAVO ~ ., data = data)
# Stepwise regression model
step.model <- stepAIC(full.model, direction = "both", 
                      trace = FALSE)

summary(step.model)

library(pROC)
predpr <- predict(full.model,type=c("response"))
roccurve <- roc(AcidRefluxBRAVO ~ predpr, data = data)
plot(roccurve)
auc(roccurve)

detach("package:MASS", unload=TRUE)
```

```{r HRM_UnivariateAnalysis}

#Univariate analysis:
NegBRAVOAndHRMFinal<-BravoAndHRMNoMissingFinal[BravoAndHRMNoMissingFinal$AcidRefluxBRAVO==1,]
PosBRAVOAndHRMFinal<-BravoAndHRMNoMissingFinal[BravoAndHRMNoMissingFinal$AcidRefluxBRAVO==0,]


#Univariate analysis
t.test(NegBRAVOAndHRMFinal$BasalrespiratoryminmmHg ,PosBRAVOAndHRMFinal$BasalrespiratoryminmmHg,paired=FALSE)

chisq.test(NegBRAVOAndHRMFinal$Hiatalhernia,PosBRAVOAndHRMFinal$Hiatalhernia)
t.test(NegImpPosBRAVOFinal$Distallatency,NegImpNegBRAVOFinal$Distallatency,paired=FALSE)
t.test(NegImpPosBRAVOFinal$largebreaks,NegImpNegBRAVOFinal$largebreaks,paired=FALSE)

```
##################################################################################################################
###################################### Nothing done from here down ######################################
##################################################################################################################
##################################################################################################################
##################################################################################################################
##################################################################################################################
##################################################################################################################
##################################################################################################################
```{r PrelimAnalysisImp}

#Use the data set loaded above
                                                                               
library(psych)
#Only select the numerical variables

#4. Get rid of bad outliers

#5. Transform variables


#Select HRM only. Also get rid of DistalLESfromnarescm,ProximalLESfromnarescm,EsophageallengthLESUEScenterscm as these are colinear and reflect length of oesophagus altogether)

#4. Variable selection- choose HRM variables only here. Got rid of BasalrespiratorymeanmmHg,ContractileFrontVelocity,HiatusHernia and most oesophageal length measurements because of colinearity concerns with other variables

#Variables removed: MainReflxSettingsAnalysisDurationUpright(as is a 24 hour clock) 
#MainAcidCompositeScorePatientValueRecumbentTimeInReflux,
#MainAcidCompositeScorePatientValueEpisodesOver5min,
#MainAcidCompositeScorePatientValueLongestEpisode,
#MainAcidCompositeScorePatientValueTotalEpisodes,
#MainAcidCompositeScorePatientScoreTotalEpisodes,
#MainAcidCompositeScorePatientScoreUprightTimeInReflux,
#MainAcidCompositeScorePatientScoreRecumbentTimeInReflux,
#MainAcidCompositeScorePatientScoreTotalTimeInReflux,
#MainAcidCompositeScorePatientScoreEpisodesOver5min,
#MainAcidCompositeScorePatientScoreLongestEpisode,
#MainAcidCompositeScorePatientValueUprightTimeInReflux,(all the composite scores are likely to be related to the other scores anyway)
#MainPPPostprandExpoAnalysisDurationUpright,
#MainPPPostprandExpoAnalysisDurationRecumbent,
#MainPPPostprandExpoAnalysisDurationTotal,
#MainReflxSettingsAnalysisDurationRecumbent,
#MainReflxSettingsAnalysisDurationTotal,(all the duration are 24 hour clock times)
#MainAcidExpUprightGastricChannelTimepHLessThan40, (gastric channel unlikely to be relevant)
#MainAcidExpRecumbentGastricChannelTimepHLessThan40, (gastric channel unlikely to be relevant)

#Postprandial exclude for now:
# MainPPBolusExpoAcidPercentTime,
# MainPPBolusExpoNonacidTime,
# MainPPBolusExpoNonacidPercentTime,
# MainPPBolusExpoAllRefluxTime,
# MainPPBolusExpoAllRefluxPercentTime,
# MainPPBolusExpoMedianBolusClearanceTime,
# PPReflEpisodeActExpoAcid,
# PPReflEpisodeActExpoNonacid,
# PPReflEpisodeActExpoAllReflux,
# MainPPBolusExpoAcidTime,
# MainPPAcidExpoClearanceChannelNumberofAcidEpisodes,
# MainPPAcidExpoClearanceChannelTime,
# MainPPAcidExpoClearanceChannelPercentTime,
# MainPPAcidExpoClearanceChannelMeanAcidClearanceTime,
# MainPPAcidExpoClearanceChannelLongestEpisode,
# MainPPAcidExpoGastricChannelPercentTime,
# MainAcidExpTotalGastricChannelTimepHLessThan40,

# MainRflxEpisodeUprightAcid,
# MainRflxEpisodeRecumbentAcid,
# MainRflxEpisodeTotalAcid,
# MainRflxEpisodeUprightNonacid,
# MainRflxEpisodeRecumbentNonacid,
# MainRflxEpisodeTotalNonacid,
# MainRflxEpisodeUprightAllReflux,
# MainRflxEpisodeRecumbentAllReflux,
# MainRflxEpisodeTotalAllReflux,

#This lot likely to already be represented under PercentTime
# MainAcidExpUprightClearanceChannelTime,
# MainAcidExpRecumbentClearanceChannelTime,
# MainAcidExpTotalClearanceChannelTime,
# MainAcidExpUprightClearanceChannelMeanAcidClearanceTime,
# MainAcidExpRecumbentClearanceChannelMeanAcidClearanceTime,
# MainAcidExpTotalClearanceChannelMeanAcidClearanceTime,

# Colinearity issues:
# MainAcidExpUprightClearanceChannelPercentTime,
# MainAcidExpUprightClearanceChannelNumberofAcidEpisodes,

# Don't seem to be contributing much to the model:
# MainAcidExpRecumbentClearanceChannelLongestEpisode
# MainAcidExpTotalClearanceChannelLongestEpisode

NegImpALL_BRAVO_WithImpNoMissing<- NegImpALL_BRAVO_WithImpAndHRMNoMissing %>% 
    ungroup()%>%
select(
MainAcidExpRecumbentClearanceChannelNumberofAcidEpisodes,
MainAcidExpTotalClearanceChannelNumberofAcidEpisodes,
MainAcidExpRecumbentClearanceChannelPercentTime,
MainAcidExpTotalClearanceChannelPercentTime,
MainAcidExpUprightClearanceChannelLongestEpisode,
MainAcidCompositeScorePatientValueTotalTimeInReflux,
MainAcidCompositeScorePatientValueRecumbentTimeInReflux,
MainAcidCompositeScorePatientValueUprightTimeInReflux,
AcidRefluxBRAVO)

NegImpALL_BRAVO_WithImpNoMissing<-dplyr::select_if(NegImpALL_BRAVO_WithImpNoMissing, is.numeric)

#Check for multicolinearity
library("PerformanceAnalytics")
chart.Correlation(NegImpALL_BRAVO_WithImpNoMissing, histogram=FALSE, pch=1)
cor(NegImpALL_BRAVO_WithImpNoMissing, method = "pearson", use = "complete.obs")

#Exploratory data analysis:
create_report(NegImpALL_BRAVO_WithImpNoMissing)

#Consider changing variables and repeat step 4
```

```{r Imp_MultipleLogRegression}



#Running multivariate analysis
library(MASS)
# Fit the full model 
data<-na.omit(NegImpALL_BRAVO_WithImpNoMissing)
full.model <- glm(AcidRefluxBRAVO ~ ., data = data)
# Stepwise regression model
step.model <- stepAIC(full.model, direction = "both", trace = FALSE)
summary(step.model)

library(pROC)
predpr <- predict(full.model,type=c("response"))
roccurve <- roc(AcidRefluxBRAVO ~ predpr, data = data)
plot(roccurve)
auc(roccurve)

detach("package:MASS", unload=TRUE)
```

```{r Imp_UnivariateAnalysis}


#Univariate analysis:
NegImpPosBRAVO<-NegImpALL_BRAVO_WithImpNoMissing[NegImpALL_BRAVO_WithImpNoMissing$AcidRefluxBRAVO==1,]
NegImpNegBRAVO<-NegImpALL_BRAVO_WithImpNoMissing[NegImpALL_BRAVO_WithImpNoMissing$AcidRefluxBRAVO==0,]


#3. Check normality
library(ggpubr)
ggqqplot(NegImpPosBRAVO$PIPfromnarescm)


#Univariate analysis
t.test(NegImpPosBRAVO$MainAcidExpUprightClearanceChannelLongestEpisode,NegImpNegBRAVO$MainAcidExpUprightClearanceChannelLongestEpisode,paired=FALSE)

#Get a ROC curve
library(ROCR)
prediction( NegImpALL_BRAVO_WithImpNoMissing$MainAcidExpUprightClearanceChannelLongestEpisode, NegImpALL_BRAVO_WithImpNoMissing$AcidRefluxBRAVO)

perf1 <- performance(pred, "sens", "spec")
plot(perf1)

library(OptimalCutpoints)
NegImpALL_BRAVO_WithImpNoMissing<-data.frame(NegImpALL_BRAVO_WithImpNoMissing,stringsAsFactors = F)
optimal.cutpoints(X="MainAcidCompositeScorePatientValueUprightTimeInReflux",status="AcidRefluxBRAVO",tag.healthy=1,methods = "Youden",data=NegImpALL_BRAVO_WithImpNoMissing, pop.prev = NULL,
control = control.cutpoints(), ci.fit = FALSE, conf.level = 0.95, trace = FALSE)


```

```{r PrelimAnalysisImpAndHRM}

NegImpALL_BRAVO_WithImpNoMissing$failedChicagoClassification<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$failedChicagoClassification)
NegImpALL_BRAVO_WithImpNoMissing$panesophagealpressurization<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$panesophagealpressurization)
NegImpALL_BRAVO_WithImpNoMissing$largebreaks<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$largebreaks)
NegImpALL_BRAVO_WithImpNoMissing$prematurecontraction<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$prematurecontraction)
NegImpALL_BRAVO_WithImpNoMissing$rapidcontraction<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$rapidcontraction)
NegImpALL_BRAVO_WithImpNoMissing$smallbreaks<-as.factor(NegImpALL_BRAVO_WithImpNoMissing$smallbreaks)

NegImpALL_BRAVO_WithImpNoMissing<- NegImpALL_BRAVO_WithImpAndHRMNoMissing %>%  
  ungroup()%>%
  select(
IntraabdominalLESlengthcm,
 Hiatalhernia,
         LOS_relax,
         LowerOesoph,
BasalrespiratoryminmmHg,
ResidualmeanmmHg,
DistalcontractileintegralmeanmmHgcms,
IntraboluspressureATLESRmmHg,
Distallatency,
failedChicagoClassification,
panesophagealpressurization,
largebreaks,
prematurecontraction,
rapidcontraction,
smallbreaks,
MainAcidExpRecumbentClearanceChannelNumberofAcidEpisodes,
MainAcidExpTotalClearanceChannelNumberofAcidEpisodes,
MainAcidExpRecumbentClearanceChannelPercentTime,
MainAcidExpTotalClearanceChannelPercentTime,
MainAcidExpUprightClearanceChannelLongestEpisode,
MainAcidCompositeScorePatientValueTotalTimeInReflux,
MainAcidCompositeScorePatientValueRecumbentTimeInReflux,
MainAcidCompositeScorePatientValueUprightTimeInReflux,
AcidRefluxBRAVO)


NegImpALL_BRAVO_WithImpNoMissing<-dplyr::select_if(NegImpALL_BRAVO_WithImpNoMissing, is.numeric)


#Check for multicolinearity
library("PerformanceAnalytics")
chart.Correlation(NegImpALL_BRAVO_WithImpNoMissing, histogram=FALSE, pch=1)
cor(NegImpALL_BRAVO_WithImpNoMissing, method = "pearson", use = "complete.obs")

#Exploratory data analysis:
create_report(NegImpALL_BRAVO_WithImpNoMissing)

```

```{r ImpAndHRM_LogisticRegression}



library(MASS)
# Fit the full model 
data<-na.omit(NegImpALL_BRAVO_WithImpNoMissing)
full.model <- glm(AcidRefluxBRAVO ~ ., data = data)
# Stepwise regression model
step.model <- stepAIC(full.model, direction = "both", trace = FALSE)
summary(step.model)

library(pROC)
predpr <- predict(full.model,type=c("response"))
roccurve <- roc(AcidRefluxBRAVO ~ predpr, data = data)
plot(roccurve)
auc(roccurve)

detach("package:MASS", unload=TRUE)


```

```{r ImpAndHRM_UnivariateAnalysis}
#Univariate analysis:
NegImpPosBRAVO<-NegImpALL_BRAVO_WithImpNoMissing[NegImpALL_BRAVO_WithImpNoMissing$AcidRefluxBRAVO==1,]
NegImpNegBRAVO<-NegImpALL_BRAVO_WithImpNoMissing[NegImpALL_BRAVO_WithImpNoMissing$AcidRefluxBRAVO==0,]


t.test(NegImpPosBRAVO$Distallatency,NegImpNegBRAVO$Distallatency,paired=FALSE)


```

```{r VarDiagram}
#### Documenting the sets 

nodes <- create_node_df(n=6, 
                        nodes=c("ImpAll", "AllBravo", "NegativeImpedance","MyBravoFromNegativeImpedance","MyBravoFromNegativeImpedancePOSITIVE_BRAVO","MyBravoFromNegativeImpedanceNEGATTIVE_BRAVO"),
                        label=c(paste0("ImpAll: ",nrow(ImpAll)), stringr::str_wrap(paste0("All BRAVO: ",nrow(AllBravo)),10), stringr::str_wrap(paste0("Negative Impedance: ",nrow(NegativeImpedance)),10),
                                stringr::str_wrap(paste0("MyBravo (Negative Impedance):",nrow(MyBravoFromNegativeImpedance)),10),
                                stringr::str_wrap(paste0("Positive BRAVO:",nrow(MyBravoFromNegativeImpedancePOSITIVE_BRAVO)),10),
                                stringr::str_wrap(paste0("Negative BRAVO: ",nrow(MyBravoFromNegativeImpedanceNEGATTIVE_BRAVO)),10)),
                        shape = "rectangle",
                        fontsize=5)

edges <-
  create_edge_df(
    from = c(1,2,3,4,4),
    to = c(3,4,4,5,6))


g <- create_graph(nodes_df=nodes, 
                  edges_df=edges)%>%
   add_global_graph_attrs(
      attr = c("layout", "rankdir", "splines"),
      value = c("dot", "TB", "false"),
      attr_type = c("graph", "graph", "graph"))
render_graph(g)

```

```{r CodeGraph}
####Documenting the code: 

# library(CodeDepends)
# sc = readScript("/home/rstudio/PhysiMineR/Questions/ImpedanceQues/NegImpBRAVO/NegativeImpedanceBRAVO.Rmd")
# g = makeVariableGraph( info =getInputs(sc))
# if(require(Rgraphviz))
#   edgemode(g) <- "directed"
# x <- layoutGraph(g, layoutType="neato")
# zz = layoutGraph(g)
# graph.par(list(nodes = list(fontsize = 100)))
# renderGraph(zz)


```

## Results


**$\color{red}{\text{I.Define the Statistical methods}}$.**

**eg** Clinical isolates of MRSP cases (n = 150) and methicillin-susceptible S. pseudintermedius (MSSP) controls (n = 133) and their corresponding host signalment and medical data covering the six months prior to staphylococcal isolation were analysed by multivariable logistic regression.

The identity of all MRSP isolates was confirmed through demonstration of S. intermedius-group specific nuc and mecA.

**$\color{red}{\text{I.Describe demographics}}$.**
The mean age was 57.3 ± 17 years, and 62.3% of the subjects were male. 
The age-adjusted incidence rates were 13.8 (non-lobar) and 4.9 (lobar) per 100,000 person-years.
**$\color{red}{\text{J.Then describe level one results}}$.**

**$\color{red}{\text{K.Then describe subset results}}$.**

**eg** In the final model, cats (compared to dogs, OR 18.5, 95% CI 1.8–188.0, P = 0.01), animals that had been
hospitalised (OR 104.4, 95% CI 21.3–511.6, P < 0.001), or visited veterinary clinics more frequently (>10 visits
OR 7.3, 95% CI 1.0–52.6, P = 0.049) and those that had received topical ear medication (OR 5.1, 95% CI 1.8–
14.9, P = 0.003) or glucocorticoids (OR 22.5, 95% CI 7.0–72.6, P < 0.001) were at higher risk of MRSP infection,
whereas S. pseudintermedius isolates from ears were more likely to belong to the MSSP group (OR 0.09, 95%
CI 0.03–0.34, P < 0.001).

**Choose your statistical analysis**


```{r Results}
######################################### Data analysis######################################### 




```

## Discussion

**$\color{red}{\text{L.Sentence 1: To be decided}}$.**

**$\color{red}{\text{M.Sentence 2: To be decided}}$.**

**$\color{red}{\text{N.Sentence 3: To be decided}}$.**
**eg** These results indicate an association of MRSP infection with veterinary clinic/hospital
settings and possibly with chronic skin disease.


```{r Discussion}
```

## Limitations
**$\color{red}{\text{O.Sentence 1: To be decided}}$.**
**eg** There was an unexpected lack of association between MRSP and antimicrobial therapy; this requires further investigation .(Lehner et al., 2014).

```{r Limitations}
```



##Full abstract examples 

Methicillin-resistant Staphylococcus pseudintermedius (MRSP) has emerged as a highly drug-resistant small animal
veterinary pathogen. Although often isolated from outpatients in veterinary clinics, there is concern that
MRSP follows a veterinary-hospital associated epidemiology. This study’s objective was to identify risk factors for
MRSP infections in dogs and cats in Germany. Clinical isolates of MRSP cases (n = 150) and methicillin-susceptible
S. pseudintermedius (MSSP) controls (n = 133) and their corresponding host signalment and medical data
covering the six months prior to staphylococcal isolation were analysed by multivariable logistic regression. The
identity of all MRSP isolates was confirmed through demonstration of S. intermedius-group specific nuc and
mecA. In the final model, cats (compared to dogs, OR 18.5, 95% CI 1.8–188.0, P = 0.01), animals that had been
hospitalised (OR 104.4, 95% CI 21.3–511.6, P < 0.001), or visited veterinary clinics more frequently (>10 visits
OR 7.3, 95% CI 1.0–52.6, P = 0.049) and those that had received topical ear medication (OR 5.1, 95% CI 1.8–
14.9, P = 0.003) or glucocorticoids (OR 22.5, 95% CI 7.0–72.6, P < 0.001) were at higher risk of MRSP infection,
whereas S. pseudintermedius isolates from ears were more likely to belong to the MSSP group (OR 0.09, 95%
CI 0.03–0.34, P < 0.001). These results indicate an association of MRSP infection with veterinary clinic/hospital
settings and possibly with chronic skin disease. There was an unexpected lack of association between MRSP and antimicrobial therapy; this requires further investigation .(Lehner et al., 2014).

##Explanation
The abstract provides key information that enables readers to understand the key aspects of the study and decide
whether to read the article. In STROBE, item 1b recommended that authors provide an informative and balanced
summary of what experiments were done, what results were found and the implications of the findings in the abstract.
In STROBE-Vet, this item was modified to provide more guidance on the key components that should be addressed.
The study design should be stated; however, if the study does not correspond to a named study design such as case–
control, cross-sectional and cohort study, then the author should describe the key elements of the study design such
as incident versus prevalent cases, and whether or not the selection was based on outcome status (Pearce, 2012). The
abstract should succinctly describe the study objectives, including the primary objective and primary outcome, the
exposure(s) of interest, relevant population information such as species and the purpose (or uses) of the animals,
the study location and dates, and the number of study units. In addition, including the organizational level at
which the outcome was measured (e.g. herd, pen or individual) is recommended. The presented results should
include summary outcome measures (e.g. frequency or appropriate descriptor of central tendency such as mean or
median) and, if relevant, a clear description of the association direction along with accompanying association measures
(e.g. odds ratio) and measures of precision (e.g. 95% confidence interval) rather than P-value alone. We discourage
stating that an exposure is or is not significantly associated with an outcome without appropriate statistical
measures. Finally, because many veterinary observational studies evaluate multiple potential risk factors, the abstract
should provide the number of exposure–outcome associations tested to alert the end-user to potential type I error in
the study. When multiple outcomes are observed, provide the reader with a rationale for the outcomes presented in
the abstract, for example only statistically significant results or the outcome of the primary hypothesis is presented.






##Other examples of good abstracts:

 Lymphoma in patients treated with anti-TNF: results of the 3-year prospective French RATIO registry
 X Mariette1, F Tubach2, H Bagheri3, M Bardet4, J M Berthelot5, P Gaudin6, D Heresbach7, A Martin8, T
 Schaeverbeke9, D Salmon10, M Lemann11, O Hermine12, M Raphael13, P Ravaud2
 
 Author affiliations
 
 Abstract
 
 **Objective:** To describe cases of lymphoma associated with anti-TNF therapy, identify risk factors,
 estimate the incidence and compare the risks for different anti-TNF agents.

 **Methods:** A national prospective registry was designed (Research Axed on Tolerance of bIOtherapies; RATIO)
 to collect all cases of lymphoma in French patients receiving anti-TNF therapy from 2004 to 2006, whatever
 the indication. A case–control analysis was conducted including two controls treated with anti-TNF per case
 and an incidence study of lymphoma with the French population was used as the reference.

 **Results:** 38 cases of lymphoma, 31 non-Hodgkin’s lymphoma (NHL) (26 B cell and five T cell), five Hodgkin’s
 lymphoma (HL) and two Hodgkin’s-like lymphoma were collected. Epstein–Barr virus was detected in both of two
 Hodgkin’s-like lymphoma, three of five HL and one NHL. Patients receiving adalimumab or infliximab had a higher
 risk than those treated with etanercept: standardised incidence ratio (SIR) 4.1 (2.3–7.1) and 3.6 (2.3–5.6)
 versus 0.9 (0.4–1.8). The exposure to adalimumab or infliximab versus etanercept was an independent risk factor
 for lymphoma in the case–control study: odds ratio 4.7 (1.3–17.7) and 4.1 (1.4–12.5), respectively. The sex and
 age-adjusted incidence rate of lymphoma was 42.1 per 100 000 patient-years. The SIR was 2.4 (95% CI 1.7 to 3.2).

 **Conclusion:** The two to threefold increased risk of lymphoma in patients receiving anti-TNF therapy is similar
 to that expected for such patients with severe inflammatory diseases. Some lymphomas associated with
 immunosuppression may occur, and the risk of lymphoma is higher with monoclonal-antibody therapy than with
 soluble-receptor therapy.


 http://dx.doi.org/10.1136/ard.2009.117762


 Most studies investigating the association between psoriasis and cardiovascular disease
 have shown a significant relationship. This comparison study investigated the association
 between psoriasis and prevalent use of cardiovascular drugs. Drug exposure data for 1998 to
 2006 were extracted from the Dutch PHARMO-Record Linkage System database. Psoriasis patients were
 selected using an algorithm of hospitalization and drug dispensing records specific for psoriasis and
 matched with controls for gender, age and time-period. From the records of 2.5 million Dutch residents,
 9,804 (0.4%) psoriasis patients and 15,288 (0.6%) controls were selected. Psoriasis patients used
 significantly more anti-hypertensives, anti-coagulant and anti-platelet agents, digoxin, nitrates,
 lipid-lowering and anti-diabetic drugs than the reference population during a 5-year period observation.
 In a multiple linear regression model adjusting for the number of unique drugs used, psoriasis was no longer
 significantly associated with any of these drug classes. Psoriasis patients used more cardiovascular-related
 drugs, but surveillance bias appears to affect this association considerably.






 **Background:** The incidence of intracerebral haemorrhage (ICH) in Hispanics is high,
 especially of non-lobar ICH. Our aim was to ascertain prospectively the incidence of
 first-ever spontaneous ICH (SICH) stratified by localisation in a Hispanic-Mestizo
 population of the north of Chile. Methods: Between July 2000 and June 2002 all possible
 cases of ICH were ascertained from multiple overlapping sources. The cases were allocated
 according to localisation. Those with vascular malformations or non-identifiable localisations
 were excluded. Results: We identified a total of 69 cases of first-ever ICH. Of these, 64 (92.7%)
 had SICH, of which we allocated 58 cases (84%) to non-lobar or lobar localisation. The mean age
 was 57.3 ± 17 years, and 62.3% of the subjects were male. The age-adjusted incidence rates were 13.8
 (non-lobar) and 4.9 (lobar) per 100,000 person-years. Non-lobar SICH was more frequent in young
 males and lobar SICH in older women. The non-lobar-to-lobar ratio was similar to previous findings
 in Hispanics. Hypertension was more frequent in non-lobar SICH and in diabetes, heavy drinking and
 antithrombotic use in lobar SICH, but in none significantly. There was no association between
 localisation and prognosis. Conclusions: The incidence of non-lobar SICH was high, but lower than
 in most non-white populations. This lower incidence could be due to a lower population prevalence of
 risk factors, a higher socioeconomic level in this population, or chance.



